---
title       : Stock Trend App
subtitle    : ShinyApp
author      : Sandhya K Prasad
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [bootstrap, quiz, shiny, interactive]     # {mathjax, quiz, bootstrap,shiny,interactive}
ext_widgets: {rCharts: [libraries/nvd3]}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Stock Trend App Key Features

1. Easy and Intuitive User InterFace.
2. Fetches the stock quote over a date range .
3. Displays the stock price Trend using a Plot.
4. Calculates and displays the stock percent change for the provided date range.
5. Displays the retrieved information of the stock as a table. 

---

## App in Action

```{r opts.label='shiny'}
slidifyUI(
        sidebarPanel(
                selectInput('symbol','Choose Symbol',c("AAPL","GOOG","FB","VZ","TSLA","TWTR"))
                
         ),
        mainPanel(
                tags$div(id='plot',class='shiny-html-output nvd3 rChart'),
                h3(textOutput("percentChange"),align="center")
                
        )
        
)
```

---
## NVD3 Plot Inline

```{r nvd3plot, results = 'asis', comment = NA, message = F, echo = F}
require(rCharts)
n1 <- nPlot(mpg ~ wt, data = mtcars, type = 'scatterChart')
n1$show('inline')
```

---
## Design Of The App

1. Designed using R **Shiny** Application.
2. Stock Quote Data retrieval is powered by the **Quantmod** R package .
3. Data source is obtained from **Yahoo Finance** Data .
4. Application is served by the **shinyapps.io** server.
5. These slides are generated using **slidify** and **rCharts** packages.

---

## Quick Links

1. [Stock Price Trend App](https://sandykp.shinyapps.io/StockTrendApp/)

2. [Documentation](https://sandykp.shinyapps.io/StockTrendApp/stockTrendShinyApp.html)

3. [Github Code Repository](https://github.com/Sandhyakprasad/DevelopingDataProducts.git)





